---
title: "Reproducibility appendix"
---

Every number in this book is reproducible from code. This appendix explains how the checks
were built, states the verification standard, and lists the shared tools and the environment.

## How the checks were built

Each chapter's figure runs a small simulation that implements **the dissertation's own
equations** — the PC-MFRM data-generating model (Eqs. 7/8), the MFRM infit/outfit fit
statistics (Eqs. 2/3), the GPCM first stage of the HRM (Eq. 5), and the signal-detection
second stage (Eq. 6) — coded from scratch in R. **No chapter re-runs TAM or immer.** The aim
is to show how the model *as specified* behaves, so the argument never depends on reproducing
a particular software run.

Those shared equations live in one file, `R/common.R`, which every chapter sources. The
implementation was cross-checked against an independent **Python** reference written from the
same equations: on a grid of 610 probability cells plus the expected score, the score
variance, and seven scalar cases (log-likelihoods and fit statistics), the R and Python
implementations agree to **≈ 2 × 10⁻¹⁴** — machine precision. So any difference between a
chapter's R figure and that reference comes only from Monte-Carlo draws, never from the
arithmetic.

## The verification standard

Each quantity a chapter relies on is one of two kinds:

- **Deterministic** (a seed-independent analytic fact — e.g., a slope of 0 gives exactly
  uniform category probabilities; the SDM tends to uniform as ψ → ∞; the false-positive rate
  at the +0.5 cut is $1-\Phi(1)=0.159$; an $\eta^2$ of .01 maps to AUC $\approx 0.557$). These
  must match the independent reference essentially exactly.
- **Stochastic** (a Monte-Carlo estimate — e.g., the recovered severe-rater location, the
  baseline marginal correlation, the empirical false-positive rate). These match within
  Monte-Carlo tolerance; R's RNG differs from NumPy's, so the exact draws differ while the
  conclusion does not.

The frozen reference values, with each quantity's type and tolerance, were fixed in advance, and every claim was checked against the page and quotation it
rests on in the source dissertation.

## The shared code (`R/common.R`)

```{r}
#| label: show-common
#| code-fold: true
#| code-summary: "Show R/common.R (the dissertation's equations, in R)"
#| eval: false
# The full source is reproduced here for transparency; it is the file every
# chapter sources. (eval: false — shown, not re-run.)
cat(readLines("R/common.R"), sep = "\n")
```

```{r}
#| label: common-smoke
#| code-summary: "A 3-line smoke test of the shared equations"
source("R/common.R")
# slope 0 ⇒ exactly uniform; SDM ⇒ uniform as ψ grows; both are the book's anchors
round(rbind(`PC-MFRM α=0` = as.numeric(pcmfrm_probs(0.3, alpha = 0)),
            `SDM ψ=20`    = as.numeric(sdm_probs(2, psi = 20))), 3)
```

Both rows are flat at 0.20 — the deterministic anchors behind Chapters 1 and 3.

## Random seeds and cross-checks

Each chapter's figure sets an explicit seed (visible in its code block), so every stochastic
quantity reproduces exactly on re-render. During development, each derived value was also
cross-checked against an independent Python implementation of the same equations.

## Session information

```{r}
#| label: sessioninfo
#| code-fold: true
#| code-summary: "Show R session info"
sessionInfo()
```
